Eval expressions

### 2021-02-12 analysis/expressions.Rmd
Correctly counting number of resolved_expr (use hash because of truncation)

>>>>

To check whether the normalization makes sense, we have a look at how many normalized expressions we have per call sites.
```{r}
by_src_ref <- E_cano %>% group_by(src_ref) %>%
  summarise(n_resolved = n_distinct(hash), n_canonic = n_distinct(expr_canonic))
```

There should always be less normalized epxressions than resolved ones. For how many do we have strictly less normalized expressions?

```{r}
by_src_ref %>% filter(n_resolved > n_canonic) %>% arrange(desc(n_canonic))
```

```{r}
by_src_ref %>% filter(n_resolved == 1 | n_resolved > n_canonic)  %>% arrange(desc(n_canonic)) %>% print(n = 100)
```

```{r}
exprs_by_srcref <- E_cano %>% group_by(src_ref) %>% summarize(n_canonic = n_distinct(expr_canonic), exprs = paste0(unique(expr_canonic), collapse="    ;     "))
```
